---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

# Report Details

```{r}
articleID <- 6-7-2014 # insert the article ID code here e.g., "10-3-2015"
reportType <- 'pilot' # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- 'Yuman Li' # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- 'Brendan Fereday' # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- 180 # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- 11/10/19 # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- NA # insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- NA # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

The study asked people to rate the subjective distance of some subway stations on the line that they were traveling along by using a scale from 1 (very close) to 7 (very far). People from the westbound (n = 100) or the eastbound platform (n = 100) were randomly assigned to conditions to rate the subjective distance of four stations: the Spadina station (two stops to the west), the St. George station (one stop to the west), the Bloor-Yonge station (one stop to the east), or the Sherbourne station (two stops to the east), which are either upcoming or just past stations.

------

#### Target outcomes: 

"We carried out a 2 (orientation: toward, away from) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) analysis of variance (ANOVA) on closeness ratings, which revealed no main effect of orientation, F < 1, and a main effect of station, F(3, 194) = 24.10, p < .001, ηp2 = .27. This main effect was qualified by the predicted interaction between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20. We decomposed this interaction by the subjective-distance ratings between participants traveling east and west for each of the four subway stations. Westbound participants rated the stations to the west of Bay Street as closer than did eastbound participants; this effect was obtained for both the station one stop to the west (St. George, p < .001, ηp2 = .28) and the station two stops to the west (Spadina, p = .001, ηp2 = .20). The opposite pattern held true for stations to the east of Bay Street. Eastbound participants rated the stations to the east of Bay Street as closer than did westbound participants; this effect was obtained for both the station one stop to the east (Bloor-Yonge, p = .053, ηp2 = .08) and the station two stops to the east (Sherbourne, p < .001, ηp2 = .24)."

------

```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object

```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(lsr)
```


```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
d <- read_excel('GroupB_6-7-2014/data/S1_Subway.xlsx')
```

# Step 3: Tidy data

```{r}

```

# Step 4: Run analysis

## Pre-processing

```{r}
```

## Descriptive statistics

```{r}
d_descriptive = d %>% 
  group_by(DIRECTION,STN_NAME) %>%
  summarise(meanDistance = mean(DISTANCE),stdDistance = sd(DISTANCE))
d_descriptive
```

## Inferential statistics

"We carried out a 2 (orientation: toward, away from) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) analysis of variance (ANOVA) on closeness ratings, which revealed no main effect of orientation, F < 1, and a main effect of station, F(3, 194) = 24.10, p < .001, ηp2 = .27. This main effect was qualified by the predicted interaction between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20."

```{r}
model = aov (DISTANCE ~ DIRECTION*STN_NAME, data = d)
summary (model)
etaSquared (model)

#check values

#no main effect of orientation
direction_F <- 0.664 
reportObject <- reproCheck(reportedValue = '<1', obtainedValue = direction_F, valueType = 'F', eyeballCheck = TRUE )

# a main effect of station
station_F <- 23.349
reportObject <- reproCheck(reportedValue = '24.10', obtainedValue = station_F, valueType = 'F', eyeballCheck = TRUE )
station_p <- 6.01e-13
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = station_p, valueType = 'p', eyeballCheck = TRUE )
station_eta <- 0.265284110
reportObject <- reproCheck(reportedValue = '.27', obtainedValue = station_eta, valueType = 'other', eyeballCheck = TRUE )

# interaction between orientation and station
interaction_F <- 16.283
reportObject <- reproCheck(reportedValue = '16.28', obtainedValue = interaction_F, valueType = 'F', eyeballCheck = TRUE )
interaction_p <- 1.77e-09
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = interaction_p, valueType = 'p', eyeballCheck = TRUE )
```
"We decomposed this interaction by the subjective-distance ratings between participants traveling east and west for each of the four subway stations. Westbound participants rated the stations to the west of Bay Street as closer than did eastbound participants; this effect was obtained for both the station one stop to the west (St. George, p < .001, ηp2 = .28) and the station two stops to the west (Spadina, p = .001, ηp2 = .20). The opposite pattern held true for stations to the east of Bay Street. Eastbound participants rated the stations to the east of Bay Street as closer than did westbound participants; this effect was obtained for both the station one stop to the east (Bloor-Yonge, p = .053, ηp2 = .08) and the station two stops to the east (Sherbourne, p < .001, ηp2 = .24)."

```{r}
#divide data from four stations into four groups:
St.George = d %>%
  filter (STN_NAME == 'STG')
Spadina = d %>%
  filter (STN_NAME == 'SPAD')
BloorYonge = d %>%
  filter (STN_NAME  == 'B-Y')
Sherbourne = d %>%
  filter (STN_NAME == 'SHER')
```

```{r}
#check values for each group

#St.George
model1 = aov(DISTANCE ~ DIRECTION, data = St.George)
summary(model1)
etaSquared(model1)
St.George_p <- 7.23e-05
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = St.George_p, valueType = 'p', eyeballCheck = TRUE )
St.George_eta <- 0.2772092
reportObject <- reproCheck(reportedValue = '.28', obtainedValue = St.George_eta, valueType = 'other', eyeballCheck = TRUE )

#Spadina
model2 = aov(DISTANCE ~ DIRECTION, data = Spadina)
summary(model2)
etaSquared(model2)
Spadina_p <- 0.00113
reportObject <- reproCheck(reportedValue = '.001', obtainedValue = Spadina_p, valueType = 'p', eyeballCheck = TRUE )
Spadina_eta <- 0.1962763
reportObject <- reproCheck(reportedValue = '.20', obtainedValue = Spadina_eta, valueType = 'other', eyeballCheck = TRUE )

#BloorYonge
model3 = aov(DISTANCE ~ DIRECTION, data = BloorYonge)
summary(model3)
etaSquared(model3)
BloorYonge_p <- 0.0528
reportObject <- reproCheck(reportedValue = '.053', obtainedValue = BloorYonge_p, valueType = 'p', eyeballCheck = TRUE )
BloorYonge_eta <- 0.0774451
reportObject <- reproCheck(reportedValue = '.08', obtainedValue = BloorYonge_eta, valueType = 'other', eyeballCheck = TRUE )

#Sherbourne
model4 = aov(DISTANCE ~ DIRECTION, data = Sherbourne)
summary(model4)
etaSquared(model4)
Sherbourne_p <- 0.000305
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = Sherbourne_p, valueType = 'p', eyeballCheck = TRUE )
Sherbourne_eta <- 0.2356667
reportObject <- reproCheck(reportedValue = '.24', obtainedValue = Sherbourne_eta, valueType = 'other', eyeballCheck = TRUE )
```



# Step 5: Conclusion

This reproducibility check was a success.

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
